\bf Model Visualization Techniques for a Social Network Model

### 2017-05-09 paper.Rnw
just push some stuff.

@@

# running Siena
friendship <- sienaDependent(friendshipData)
alcohol <- varCovar(drink[20:35,])
mydata <- sienaDataCreate(friendship, alcohol)
myeffnull <- getEffects(mydata)
myalgorithm <- sienaAlgorithmCreate(projname = 's16_3')
set.seed(823746)
load("data/ansnullpaper.rda")
ansnullchains <- get_chain_info(ansnull)
ansnullchains %>%
  filter(period == 1) %>%  #only look at chains from wave 1 to wave 2
  group_by(rep) %>%
  select(rep, from = ego, to = alter) %>%
  mutate(val = as.numeric(!from == to),
         from = paste0("V", parse_number(from)+1), # make the chains
         to = paste0("V", parse_number(to)+1)) -> ansnullchainsw1w2
colnames(fd2.w1) <- paste0("V", 1:16)
rownames(fd2.w1) <- paste0("V", 1:16)
wave1friends <- fortify(as.adjmat(fd2.w1))
ms1 <- listMicrosteps(dat = wave1friends,
                      microsteps = filter(ansnullchainsw1w2, rep == 1))
microsteps <- ms1[1:20]

>>>>

\subsection{Model Goodness-of-Fit}

The \texttt{RSiena} software that fits the models to data also comes equipped with the \verbatim{sienaGOF()} function for examining model fit. This function ``assess[es] the fit of the model with respect to auxiliary statistics of networks" \citep[p.~53]{RSienamanual}. Examples of the auxiliary statistics are the out- or indegree distribution on the nodes, with the option for users to create their own.

@@

# running Siena
#friendship <- sienaDependent(friendshipData)
#alcohol <- varCovar(drink[20:35,])
#mydata <- sienaDataCreate(friendship, alcohol)
#myeffnull <- getEffects(mydata)
#myalgorithm <- sienaAlgorithmCreate(projname = 's16_3')
set.seed(823746)
load("data/ansnullpaper.rda")
ansnullchains <- get_chain_info(ansnull)
ansnullchains %>%
  filter(period == 1) %>%  #only look at chains from wave 1 to wave 2
  group_by(rep) %>%
  select(rep, from = ego, to = alter) %>%
  mutate(val = as.numeric(!from == to),
         from = paste0("V", parse_number(from)+1), # make the chains
         to = paste0("V", parse_number(to)+1)) -> ansnullchainsw1w2
colnames(fd2.w1) <- paste0("V", 1:16)
rownames(fd2.w1) <- paste0("V", 1:16)
wave1friends <- fortify(as.adjmat(fd2.w1))
ms1 <- listMicrosteps(dat = wave1friends,
                      microsteps = filter(ansnullchainsw1w2, rep == 1))
microsteps <- ms1[1:20]
